---
title: "port9"
author: "Yoo Ri Hwang"
date: "4/19/2022"
output: github_document
---

# overview 

K fold cross validation.

cross validation: resampling agian and agian to evaluate models (especially machine laerning models) 
K: given data is splited into "k" group

More specifically, the data is splited into training set Vs. test set.
In other words, it is splited and each splited data would be either exploration data or confiramiton data. 

# practice
## load packages 
```{r}

library(psych)  
library(tidyverse)  
library(car)

```
## load data
```{r}
filepath <- "https://quantdev.ssri.psu.edu/sites/qdev/files/apexpos.csv"
dat <- read.csv(file=url(filepath),header=TRUE)

summary(dat)

```

## Predicted model 1

yi = beta0*1 + beta1*xi

```{r}

lm <- lm(fsiq7 ~ 1 + apexpos , data=dat, na.action=na.exclude)
summary(lm)

```

## predicted model 2

yi = beta0 *1 + beta1*xi + beta2*xi^2 + ei

it is quadratic model. 

```{r}

dat$apexpos_sq <- dat$apexpos^2

lm2 <- lm(fsiq7 ~ 1 + apexpos + apexpos_sq, data=dat, na.action=na.exclude)
summary(lm2)

```

# K-fold cross vailidation ( I will choose 10 fold)



```{r}

# shuffling data
dat.shuffled<-dat[sample(nrow(dat)),]

# set k
k<-10

# creat k folds-- equal size each

folds<-cut(seq(1,nrow(dat.shuffled)),breaks=k, labels =F)
folds

```


```{r}

order <- 2 # we only have two models, with one is not quadric, and one is quadric.
k<-10

```



### practice nested for function and unfamiliar function

```{R}

# nested for
for (k in 1:10){
  
  for(i in 1:3){
    print(paste("k=",k,"i=",i)) 
  }
  
  
}


  #which()
  
  which(dat$id==10)
```

```{r}

# create an empty holder

k<-10
order<-2
r.square<- matrix(,nrow=k,ncol=order)

# k-fold validation 
for (i in 1:k){
  
  # sgmnent data by which function, and i would be 1, 2, 3, ...10 
  testIndexes<- which(folds==i, arr.ind=T)
  testData <- dat.shuffled[testIndexes,] # this will test data set
  trainData <- dat.shuffled[-testIndexes,] # except the test dataset, it will be training data set
  
   for ( j in 1:order){
     fit.train = lm(fsiq7 ~ poly(apexpos,j), data=trainData)
      fit.test = predict(fit.train, newdata = testData)
      r.square[i,j] = cor(fit.test, testData$fsiq7, use='complete')^2
   }
}

#Averinging fit at each order

fits.kfold<-colMeans(r.square)
plot(colMeans(r.square),type='l') # l for lines 


```

Based on this graph, 1 is beter than 2 (quadric model)


## Apply this to new data

### load new data 

```{r}

filepath <- "https://quantdev.ssri.psu.edu/sites/qdev/files/apexpos_test.csv"
dat.test <- read.csv(file=url(filepath),header=TRUE)

```

```{r}

newdata.predict<-predict(lm, newdata=dat.test)
cor(dat.test$fsiq7, newdata.predict)^2

```